---
title: "Draft Report: <ENTER YOUR NAME>  "
format: docx
editor: visual
---

## Background/Motivation for the Study

\*\*If you included a personal reason for the study, you do NOT have to share that here. Include relevant reference material as needed to support background.

## Research Question and Hypothesis  

What is the research question? What do you think will happen? What are you trying to show?

## Data Description and Exploratory Data Analysis 

Read in the data. You might want to consider filtering the dataset to only include the targeted variables. Identify targeted variables HERE.

```{r}
library(NHANES)
```

Describe the observations and the general characteristics being measured in the targeted data.

```{r}
#Basic summary statistics here, sample size etc... 
```

Discuss key features of your targeted data. What is a typical value? Etc...

Visualize the relationships in your targeted variables.

```{r}
#Visualization goes here 

```

Interpret the plots here. What does it show? How does this relate/support your research question?

## Analysis (LATER)  

```{r}
#Test LATER 

```

## Conclusions (LATER) 
